---
title: "Power Law Markdown"
author: "Scott Coffin"
date: "04/10/2023"
output:   
  html_document:
    code_folding: hide
    theme: journal
    toc: yes
    toc_float: yes
    toc_depth: 6
    number_sections: true
    includes:
     # after_body: footer.html
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE,time_it = TRUE) #report
```

# Introduction
* Aim: 1 PSD per compartment (e.g., stormwater, sediment, surface water, etc.) , with all data combined
* First extrapolate to largest sample size
* Second fit (bootstrap) power law distribution
* This script plots one graph per water type with xmin & slope, both with 2x SD

NOTE: THIS SCRIPT IS USED TO DERIVE ALPHA VALUES AND INCLUDES EXAMPLE DATA FROM [ZHU ET AL 2020](https://pubs.acs.org/doi/10.1021/acsestwater.0c00292)

## Setup
```{r}
rm(list=ls()) #clear cache

#Load libraries
library(dplyr)
library(poweRlaw)
library(ggplot2)
library(ggpubr)
library(tidyverse)

## Define themes for plotting
### theme plot ####
p.theme <- theme( 
  axis.text = element_text(size = 10, colour = "black"),
  strip.text.x = element_text(size = 10, color =  "black"),
  strip.text.y = element_text(size = 10),
  axis.title = element_text(size = 10),
  panel.grid.major.x = element_blank(),
  panel.grid.major.y = element_line(size = .1, color = "grey75"),
  panel.grid.minor.y = element_line(size = .05, color = "grey85"),
  panel.grid.minor = element_blank(),
  strip.background = element_rect(fill = "white"),
  panel.border = element_rect(colour="black", size=1, fill = NA),
  panel.background = element_rect(fill = "white"),
  axis.ticks.length=unit(0.1,"cm"),
  axis.text.x  = element_text(angle = 0, hjust = 0.5),
  legend.position = "none",
  legend.box = "horizontal",
  legend.background = element_rect(fill = alpha("pink", alpha = 0)),
  legend.key = element_rect(fill = "white"),
  #legend.key.height = unit(0.5, "cm"),
  legend.key.width = unit(1.7, "cm"),
  legend.text = element_text(size = 10, colour = " black"),
  legend.title = element_blank()
)
```

## Data Import
Note: Uses example dataset which is  a  cleaned up version from Zhu et al (2020). Get file from [GitHub Repo](https://github.com/ScottCoffin/SFBayMPRiskCharacterization/blob/31fb8d8dd383fca661f983373d8a2abca4f19a50/output/data/cleanParticleData.csv). Replace with own data.

```{r}
#pull data
distributions <- read.csv("output/data/cleanParticleData.csv") #make sure to change dir

# Select only sizes with verified minimum size LOQs
sample_water <- distributions[which(distributions$Size_um <= 5000 &
                                      distributions$lower_size_limit_um >= 125 &
                                      distributions$Size_um >= 125 &
                                      distributions$MorphologicalCategory != "Fiber"),]
```

## Prepare data
```{r}
# define as factors
df <- sample_water %>% 
  mutate(matrix = as.factor(case_when(
    matrix == 'samplewater' ~ 'surface water',
    matrix == 'runoff' ~ 'stormwater',
    matrix == 'effluent' ~ 'wastewater',
    matrix == 'tissue' ~ 'tissue',
    matrix == 'sediment' ~ 'sediment'))) %>%
  drop_na(matrix) %>% 
  filter(matrix %in% c("tissue",
                       "surface water",
                       "stormwater",
                       "sediment",
                       "wastewater")) %>%
  droplevels()

#Make empty dataframes
df.bs.all <- data.frame(gof = numeric(), xmin = numeric(), pars = numeric(),
                        ntail = numeric(),watertype = numeric())

df.plot.all <- data.frame(x = numeric(), y = numeric(), watertype = numeric())
```

# Bootstrapping
This uses code provided personally from Dr. Merel Kooi, and was used in [Kooi et al.(2021)](https://www.sciencedirect.com/science/article/pii/S0043135421006278?via%3Dihub). See that paper for more details on exactly how this works.
```{r}
## bootstrap the results
for(i in unique(df$matrix)){

  df.temp <- df[which(df$matrix==i),]
  ## make into continuous powerlaw object and estimate parameters
  df.pl <- conpl$new(na.omit(df.temp$Size_um)) 
  
  ## bootstrap fit
  bs <- bootstrap(df.pl, no_of_sims = 100, 
                  threads = 2, xmax = 2E12)
  bs.res <- bs$bootstraps
  bs.res$watertype <- i
  
  ## save bootstrapped results in df 
  df.bs.all <- rbind(df.bs.all, bs.res)
  
  ## CDF results from the conpl object (makes a figure - could be turned off?)
  df.plot <- plot(df.pl)
  df.plot$watertype <- i
  
  df.plot.all<- rbind(df.plot.all, df.plot)
}


## functions to calculate mean, min and max slope
pwr <- function(x, alpha) (x/xmin.plot)^(-alpha+1)

## size range for which to generate pwr results
x <- seq(from = 125, to = 5000, by = 1)

## some empty dataframes to fill with the data that make it easier to plot

df.bs.plot <- data.frame(mean.xmin = numeric(),
                         sd.xmin = numeric(),
                         mean.alpha = numeric(),
                         sd.alpha = numeric(),
                         xmin.plot = numeric(),
                         watertype = numeric(),
                         n.obs = numeric()
)

df.pwr.plot <- data.frame(x = numeric(),
                          y = numeric(),
                          y.min = numeric(),
                          y.max = numeric(),
                          watertype = numeric())

df.pwr.plot.valid <- data.frame(x = numeric(),
                                y = numeric(),
                                y.min = numeric(),
                                y.max = numeric(),
                                watertype = numeric())


for(i in unique(df.bs.all$watertype)){
  
  ## call upon results from previous for-loop (or imported after saving)
  df.plot <- df.plot.all[which(df.plot.all$watertype == i),]
  bs.res <- df.bs.all[which(df.bs.all$watertype == i), ]
  
  ## xmin value for which the fitted function is valid (the intercept - so you can plot)
  ## first find the probability that maches with where the mean xmin intersects with the data
  ## next calculate the xmin that would fit with this probability (where would it equal 1) 
  P.xmin <- df.plot[which.min(abs(mean(bs.res$xmin)-df.plot$x)),]$y
  xmin.plot = mean(bs.res$xmin)/(P.xmin^(1/(-mean(bs.res$pars) + 1)))
  
  bs.temp <- cbind(mean(bs.res$xmin), sd(bs.res$xmin), 
                   mean(bs.res$pars), sd(bs.res$pars),
                   xmin.plot, i, nrow(df.plot))
  
  colnames(bs.temp) <- c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot", "watertype", "n.obs")
  df.bs.plot <- rbind(df.bs.plot, bs.temp)
  
  ## dataframe with values based on fitted mean bs results
  df.pwr <- data.frame(x = x, y = pwr(x, mean(bs.res$pars)))
  df.pwr$y.min <- pwr(x, mean(bs.res$pars) - 2*sd(bs.res$pars))
  df.pwr$y.max <- pwr(x, mean(bs.res$pars) + 2*sd(bs.res$pars))
  df.pwr$watertype <- i
  
  ## two dataframes, one only until xmin, the other all the way to 10 um
  df.pwr.valid <- df.pwr[which(df.pwr$x > mean(bs.res$xmin)),]
  
  df.pwr.plot <- rbind(df.pwr.plot, df.pwr)
  df.pwr.plot.valid <- rbind(df.pwr.plot.valid, df.pwr.valid)
}
#unique IDs
df.pwr.plot.all <- df.pwr.plot
df.pwr.plot.valid.all <- df.pwr.plot.valid

#lapply(df.bs.plot, class)

# ## given this + facet_wrap, we should be able to make it one figure. 
df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")] <- sapply(df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")], as.character)
df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")] <- sapply(df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")], as.numeric)


df.bs.plot$xmin.lim <- df.bs.plot$mean.xmin - 2*df.bs.plot$sd.xmin
df.bs.plot[!(df.bs.plot$xmin.lim > 1), "xmin.lim"] <- 1

#make unique ID
df.bs.plot.all <- df.bs.plot

df.bs.plot.all


#### Repeat for fish tissue only ###
### Note: I had to separate this matrix because RStudio was hitting memory limits of my laptop (Corei7, 16 GB ram). If you have a computer with more RAM, it's likely you won't have to do this janky workaround. 

fish_tissue <- distributions %>% 
  filter(Size_um <= 5000,
         Size_um >= 25,
         matrix == "tissue")

df.bs.tissue <- data.frame(gof = numeric(), xmin = numeric(), pars = numeric(),
                        ntail = numeric(),watertype = numeric())

df.plot.tissue <- data.frame(x = numeric(), y = numeric(), watertype = numeric())

df <- fish_tissue

## bootstrap the results
for(i in unique(df$matrix)){
  
  df.temp <- df[which(df$matrix==i),]
  ## make into continuous powerlaw object and estimate parameters
  df.pl <- conpl$new(na.omit(df.temp$Size_um)) 
  
  ## bootstrap fit
  bs <- bootstrap(df.pl, no_of_sims = 100, 
                  threads = 2, xmax = 2E12)
  bs.res <- bs$bootstraps
  bs.res$watertype <- i
  
  ## save bootstrapped results in df 
  df.bs.all <- rbind(df.bs.all, bs.res)
  
  ## CDF results from the conpl object (makes a figure - could be turned off?)
  df.plot <- plot(df.pl)
  df.plot$watertype <- i
  
  df.plot.all <- rbind(df.plot.all, df.plot)
}


## size range for which to generate pwr results
x <- seq(from = 25, to = 5000, by = 1)


## some empty dataframes to fill with the data that make it easier to plot

df.bs.plot <- data.frame(mean.xmin = numeric(),
                         sd.xmin = numeric(),
                         mean.alpha = numeric(),
                         sd.alpha = numeric(),
                         xmin.plot = numeric(),
                         watertype = numeric(),
                         n.obs = numeric()
)

df.pwr.plot <- data.frame(x = numeric(),
                          y = numeric(),
                          y.min = numeric(),
                          y.max = numeric(),
                          watertype = numeric())

df.pwr.plot.valid <- data.frame(x = numeric(),
                                y = numeric(),
                                y.min = numeric(),
                                y.max = numeric(),
                                watertype = numeric())


for(i in unique(df.bs.all$watertype)){
  
  ## call upon results from previous for-loop (or imported after saving)
  df.plot <- df.plot.all[which(df.plot.all$watertype == i),]
  bs.res <- df.bs.all[which(df.bs.all$watertype == i), ]
  
  ## xmin value for which the fitted function is valid (the intercept - so you can plot)
  ## first find the probability that maches with where the mean xmin intersects with the data
  ## next calculate the xmin that would fit with this probability (where would it equal 1) 
  P.xmin <- df.plot[which.min(abs(mean(bs.res$xmin)-df.plot$x)),]$y
  xmin.plot = mean(bs.res$xmin)/(P.xmin^(1/(-mean(bs.res$pars) + 1)))
  
  bs.temp <- cbind(mean(bs.res$xmin), sd(bs.res$xmin), 
                   mean(bs.res$pars), sd(bs.res$pars),
                   xmin.plot, i, nrow(df.plot))
  
  colnames(bs.temp) <- c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot", "watertype", "n.obs")
  df.bs.plot <- rbind(df.bs.plot, bs.temp)
  
  ## dataframe with values based on fitted mean bs results
  df.pwr <- data.frame(x = x, y = pwr(x, mean(bs.res$pars)))
  df.pwr$y.min <- pwr(x, mean(bs.res$pars) - 2*sd(bs.res$pars))
  df.pwr$y.max <- pwr(x, mean(bs.res$pars) + 2*sd(bs.res$pars))
  df.pwr$watertype <- i
  
  ## two dataframes, one only until xmin, the other all the way to 10 um
  df.pwr.valid <- df.pwr[which(df.pwr$x > mean(bs.res$xmin)),]
  
  df.pwr.plot <- rbind(df.pwr.plot, df.pwr)
  df.pwr.plot.valid <- rbind(df.pwr.plot.valid, df.pwr.valid)
}

#unique ID's
df.pwr.plot.tissue <- df.pwr.plot
df.pwr.plot.valid.tissue <- df.pwr.plot.valid

#join to others
df.pwr.plot.final <- rbind(df.pwr.plot.all, df.pwr.plot.tissue)
df.pwr.plot.valid.final <- rbind(df.pwr.plot.valid.all, df.pwr.plot.valid.tissue)

#lapply(df.bs.plot, class)
```

# Plot results
## Summary Table
```{r}
# ## given this + facet_wrap, we should be able to make it one figure. 
df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")] <- sapply(df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")], as.character)
df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")] <- sapply(df.bs.plot[c("mean.xmin", "sd.xmin", "mean.alpha", "sd.alpha", "xmin.plot")], as.numeric)


df.bs.plot$xmin.lim <- df.bs.plot$mean.xmin - 2*df.bs.plot$sd.xmin
df.bs.plot[!(df.bs.plot$xmin.lim > 1), "xmin.lim"] <- 1

df.bs.plot.tissue <- df.bs.plot
df.bs.plot.tissue

#join with other matrices
#df.bs.plot.final <- rbind(df.bs.plot.all, df.bs.plot.tissue)
```

#Output
## Save data
```{r}
#save
write.csv(df.bs.plot.tissue,
          "output/data/kooi/powerLaws.csv") #be sure to redefine dir
```

## Build plots
```{r}
#join plots from all and tissue
df.plot.final <- rbind(df.plot.all)#, df.plot.tissue)

## Plot the results
p <- ggplot(df.plot.final, aes(x = x, y = y)) +
  geom_point(alpha = 0.5,
             color = "black") +
  ## add xmin range (rectangle) and mean (segment)
  geom_rect(data = df.bs.plot.tissue, aes(x = NULL, y = NULL, xmin = xmin.lim, #mean.xmin - 2*sd.xmin,
                                   xmax = mean.xmin + 2*sd.xmin,
                                   ymin = 0, ymax = 1), alpha = 0.3, fill = "cadetblue4") +
  geom_segment(data = df.bs.plot.tissue, aes(x = mean.xmin, xend = mean.xmin, 
                                      y = 0, yend = 1), color = "cadetblue4", lwd = 1) +
  ## add dotted slope that goes beyond xmin
  geom_line(data = df.pwr.plot, aes(x = x, y = y), lwd = 1, color = "chocolate1", linetype = "dotted") +
  ## add line + 2*SD that stops at xmin
  geom_line(data = df.pwr.plot.valid, aes(x = x, y = y), lwd = 1, color = "chocolate3") +
  geom_ribbon(data = df.pwr.plot.valid, aes(ymin = y.min, ymax = y.max), fill = "chocolate3", alpha = 0.3) +
  xlab("Length (\U003BCm)") + ylab ("P(X >= x)") +
  scale_y_log10() + 
  scale_x_log10(breaks = c(125, 333, 1000, 3330, 5000)) +
  coord_cartesian(ylim = c(1e-3,1), xlim = c(125, 5000)) + ## cut section
  facet_wrap(~watertype, ncol = 2) +
  p.theme +
  theme(strip.text.x = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 10, colour = "black"))
p
```

## Save plots
```{r}
# save (be sure to change dir!)
ggsave(plot = p,
       filename = "powerLaws.jpg",
       path = "output/figures/kooi/", 
       width = 12, height = 9, units = "in",
       bg = "white",
       dpi = 300)
```
